### 2019-05-03 ms.tex
Typo.
Add zambia prelim results.

Finally, we complete the model by setting priors on the parameters $\beta_0, \brta_p, \beta, \rho$ and $\sigma_u$, $\sigma_v$ and $\sigma_w$.
We assigned $\rho$ and $\sigma_u$ a joint penalised complexity prior \cite{fuglstad2018constructing} such that $P(\rho < \zeta) = 0.00001$ and $P(\sigma_u > 1) = 0.00001$.
We used different $\zeta$ values for each country: Indonesia $\zeta = 3$, Senegal $\zeta = 1$ and Madagascar $\zeta = 1$.
We believe that a large proportion of the variance of malaria prevalence and incidence cannot be explained by a linear combination of the covariates selected \cite{bhatt2017improved}, so we set this prior such that the random field could explain most of the range of the data.

@@

To compare the three models we used three cross-validation schemes. 
In the first (random), the incidence data was split into ten cross-validation folds while all the prevalence data was used in each case.
%This cross-validation scheme directly addresses the question of whethe
In the second validation scheme (spatial a), the incidence data was split into spatial cross-validation folds while again all prevalence points were used in all folds.
The number of folds was seven for Indonesia, five for Senegal and three for Madagascar due to their differing sizes and epidemiological settings.
The data was divided by combining the prevalence point-survey locations and the centroids of the incidence polygons and performing k means clustering.
This scheme is specifically testing whether the joint model can improve predictions by increasing geographic data coverage.
This situation is particularly common in continental scale models where some countries will have large DHS style surveys but little incidence data.
In the final scheme (spatial b) the data is again split  spatially but the prevalence surveys from the hold-out areas are also witheld.
This scheme is testing the models' ability to predict into new areas with little information from the spatial random field.
It is therefore testing how well the models learn the parameters that relate the environment to malaria risk.

@@

\begin{table}[!t]
\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
\caption{
{\bf Summary of out-of-sample accuracy for all three cross-validation experiments.}}
\begin{tabular}{llll}
\hline
{\bf CV scheme} & {\bf Country} &  {\bf Polygons} & {\bf Joint} \\
\thickhline 
Random & Indonesia  & 13.95 &  {\bf 13.88}\\
& Senegal  & {\bf 12.41} &  12.81\\
& Madagascar  & 39.06 &  {\bf 36.36}\vspace{3mm}\\
Spatial 1 & Indonesia & {\bf 14.77} &  15.08\\
& Senegal  & {\bf 12.39} &  16.56\\
& Madagascar  & 70.72 &  {\bf 61.05}\vspace{3mm}\\
Spatial 2 & Indonesia & {\bf 14.81} &  16.36\\
& Senegal  & {\bf 12.31} &  15.91\\
& Madagascar & 67.73 &  {\bf 44.05}\\
\end{tabular}
\begin{flushleft}
Mean absolute error of predicted incidence rate against out-of-sample observed data for three countries.
\end{flushleft}
\label{table1}
\end{adjustwidth}
\end{table}

>>>>

Finally, we complete the model by setting priors on the parameters $\beta_0, \beta_p, \beta, \rho$ and $\sigma_u$, $\sigma_v$ and $\sigma_w$.
We assigned $\rho$ and $\sigma_u$ a joint penalised complexity prior \cite{fuglstad2018constructing} such that $P(\rho < \zeta) = 0.00001$ and $P(\sigma_u > 1) = 0.00001$.
We used different $\zeta$ values for each country: Indonesia $\zeta = 3$, Senegal $\zeta = 1$ and Madagascar $\zeta = 1$.
We believe that a large proportion of the variance of malaria prevalence and incidence cannot be explained by a linear combination of the covariates selected \cite{bhatt2017improved}, so we set this prior such that the random field could explain most of the range of the data.

@@

To compare the three models we used three cross-validation schemes. 
In the first (random), the incidence data was split into ten cross-validation folds while all the prevalence data was used in each case.
%This cross-validation scheme directly addresses the question of whethe
In the second validation scheme (spatial a), the incidence data was split into spatial cross-validation folds, using k means clustering on polygon centroids, while again all prevalence points were used in all folds.
The number of folds was seven for Indonesia, five for Senegal and three for Madagascar due to their differing sizes and epidemiological settings.
This scheme is specifically testing whether the joint model can improve predictions by increasing geographic data coverage.
This situation is particularly common in continental scale models where some countries will have large DHS style surveys but little incidence data.
In the final scheme (spatial b) the data is again split spatially but the prevalence surveys from the hold-out areas are also witheld.
This scheme is testing the models' ability to predict into new areas with little information from the spatial random field.
It is therefore testing how well the models learn the parameters that relate the environment to malaria risk.

@@

\begin{table}[!t]
\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
\caption{
{\bf Summary of out-of-sample accuracy for all three cross-validation experiments.}}
\begin{tabular}{llll}
\hline
{\bf CV scheme} & {\bf Country} &  {\bf Polygons} & {\bf Joint} \\
\thickhline 
Random & Indonesia  & 13.95 &  {\bf 13.88}\\
& Senegal  & {\bf 12.41} &  12.81\\
& Zambia  & {\bf 154.59} &  154.96\\
& Madagascar  & 39.06 &  {\bf 36.36}\vspace{3mm}\\
Spatial 1 & Indonesia & {\bf 14.77} &  15.08\\
& Senegal  & {\bf 12.39} &  16.56\\
& Zambia  & {\bf 162.74} &  163.74\\
& Madagascar  & 70.72 &  {\bf 61.05}\vspace{3mm}\\
Spatial 2 & Indonesia & {\bf 14.81} &  16.36\\
& Senegal  & {\bf 12.31} &  15.91\\
& Zambia  & {\bf 135.39} &  184.14\\
& Madagascar & 67.73 &  {\bf 44.05}\\
\end{tabular}
\begin{flushleft}
Mean absolute error of predicted incidence rate against out-of-sample observed data for three countries.
\end{flushleft}
\label{table1}
\end{adjustwidth}
\end{table}
